Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/conc.tex

%Conclusions
A rigorous tabulation audit is an important part of a secure election. Ballot polling RLAs are commonly used and simple, not relying on special election equipment like comparison RLAs. We present \Providence which is the most efficient and secure ballot polling RLA, as efficient as \Minerva  and flexible as \BRAVO. We present proofs and simulation results to verify the claimed properties of \Providence, and we provide an open source implementation of the stopping condition and useful related functionality.

>>>>

%Conclusions
A rigorous tabulation audit is an important part of a secure election. We present \Providence and demonstrate that it is as efficient as \Minerva and as flexible as \BRAVO. We present proofs and simulation results to verify the claimed properties of \Providence, and we provide an open source implementation of the stopping condition and useful related functionality for planning audits. We define the constraint of an acceptable probability of a misleading audit sample, and describe its importance to the planning process.
